### 2018-07-05 paper/6-engineering.tex
Add notes on Reflow and Incremental

\item[Communication] When traces or contents are stored on a central server
communication can become a bottleneck, so it is important to send only the
minimum amount of information, optimising with respect to build-system specific
invariants.

>>>>

\item[Communication] When traces or contents are stored on a central server
communication can become a bottleneck, so it is important to send only the
minimum amount of information, optimising with respect to build system
invariants. For example, incremental data processing systems in the cloud, such
as \Reflow~\cite{reflow}, need to orchestrate terabytes of data.

### 2018-07-05 paper/7-related.tex
Add notes on Reflow and Incremental

A lot of research has been dedicated to finding efficient data structures and
algorithms for self-adjusting computations~--~we plan to investigate how these
insights can be utilised by build systems as future work.

>>>>

A lot of research has been dedicated to finding efficient data structures and
algorithms for self-adjusting computations (with a few open-source
implementations, e.g. \Incremental~\cite{incremental}). We plan to investigate
how these insights can be utilised by build systems as future work.
